Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-13 paper.qmd
Updated Figure labels

# First plot with xlim and ylim
nldr_two_curvy <- nldr_two_curvy_original +
  interior_annotation("a", sc_ltr_pos, cex = 1.5) +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

hex_grid_two_curvy <- ggplot(
  data = hex_grid_with_counts, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = tsne_two_curvy_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.5, size = 0.5, color = clr_choice) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b", sc_ltr_pos, cex = 1.5)

@@

hex_grid_nonempty_two_curvy <- ggplot(
  data = hex_grid_nonempty, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = df_bin_centroids_two_curvy, 
             aes(x = c_x, y = c_y), 
             color = "#000000",
             size = 1) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("c", sc_ltr_pos, cex = 1.5) 
```

@@

trimesh_removed_two_curvy <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  coord_equal() +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("d", sc_ltr_pos, cex = 1.5)

>>>>

# First plot with xlim and ylim
nldr_two_curvy <- nldr_two_curvy_original +
  interior_annotation("a", sc_ltr_pos, cex = 2) +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

hex_grid_two_curvy <- ggplot(
  data = hex_grid_with_counts, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = tsne_two_curvy_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.5, size = 0.5, color = clr_choice) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b", sc_ltr_pos, cex = 2)

@@

hex_grid_nonempty_two_curvy <- ggplot(
  data = hex_grid_nonempty, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = df_bin_centroids_two_curvy, 
             aes(x = c_x, y = c_y), 
             color = "#000000",
             size = 1) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("c", sc_ltr_pos, cex = 2) 
```

@@

trimesh_removed_two_curvy <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  coord_equal() +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("d", sc_ltr_pos, cex = 2)
